---
title: "Mediation - Regression analyses, Unweighted"
format: docx
editor: visual
execute:
  message: false
  warning: false
---

First, we load the data and the necessary packages:

```{r}
library(here)
library(tidyverse)
library(survey)
library(srvyr)
library(marginaleffects)
library(mediation)

# for the mediation simulations
set.seed(20679593)

dat <- readRDS(file = here::here("01_data-processing", "data_private", "data_final_imputed_cases.RDS"))
```

# Regression Models

## Race -\> IPV

Without considering informal support, is race associated with different IPV rates?

```{r}
mod_race_ipv <- lm(
  formula = ipv_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat,
  
)

summary(mod_race_ipv)

marginaleffects::avg_predictions(mod_race_ipv, variables = "m_race", vcov = "HC")

marginaleffects::avg_comparisons(mod_race_ipv, variables = "m_race", vcov = "HC")
```

Without including covariates:

```{r}
mod_race_ipv_nocov <- lm(
  formula = ipv_prop ~ m_race,
  data = dat,
  
)

summary(mod_race_ipv_nocov)

marginaleffects::avg_predictions(mod_race_ipv_nocov, variables = "m_race", vcov = "HC")

marginaleffects::avg_comparisons(mod_race_ipv_nocov, variables = "m_race", vcov = "HC")
```

## Race -\> Informal Support

Is race associated with different informal support rates?

```{r}
mod_race_informal_support <- lm(
  formula = informal_support_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat,
  
)

summary(mod_race_informal_support)

marginaleffects::avg_predictions(mod_race_informal_support, variables = "m_race", vcov = "HC")
marginaleffects::avg_comparisons(mod_race_informal_support, variables = "m_race", vcov = "HC")
```

Without including covariates:

```{r}
mod_race_informal_support_nocov <- lm(
  formula = informal_support_prop ~ m_race,
  data = dat,
  
)

summary(mod_race_informal_support_nocov)

marginaleffects::avg_predictions(mod_race_informal_support_nocov, variables = "m_race", vcov = "HC")
marginaleffects::avg_comparisons(mod_race_informal_support_nocov, variables = "m_race", vcov = "HC")
```

## Race + Informal Support -\> IPV

When using race and informal support, are they, respectively, predictive of IPV?

```{r}
mod_race_informal_support_ipv <- lm(
  formula = ipv_prop ~ m_race + informal_support_prop +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat,
  
)

summary(mod_race_informal_support_ipv)

marginaleffects::avg_predictions(mod_race_informal_support_ipv, variables = "m_race", vcov = "HC")

marginaleffects::avg_predictions(mod_race_informal_support_ipv, variables = c("m_race", "informal_support_prop"), vcov = "HC")


marginaleffects::avg_comparisons(mod_race_informal_support_ipv, variables = "m_race", vcov = "HC")


marginaleffects::avg_predictions(mod_race_informal_support_ipv, variables = "informal_support_prop", vcov = "HC")

marginaleffects::avg_comparisons(mod_race_informal_support_ipv, variables = list("informal_support_prop" = "minmax"), vcov = "HC")
```

Without including covariates:

```{r}
mod_race_informal_support_ipv_nocov <- lm(
  formula = ipv_prop ~ m_race + informal_support_prop ,
  data = dat,
  
)

summary(mod_race_informal_support_ipv_nocov)

marginaleffects::avg_predictions(mod_race_informal_support_ipv_nocov, variables = "m_race", vcov = "HC")

marginaleffects::avg_predictions(mod_race_informal_support_ipv_nocov, variables = c("m_race", "informal_support_prop"), vcov = "HC")


marginaleffects::avg_comparisons(mod_race_informal_support_ipv_nocov, variables = "m_race", vcov = "HC")


marginaleffects::avg_predictions(mod_race_informal_support_ipv_nocov, variables = "informal_support_prop", vcov = "HC")

marginaleffects::avg_comparisons(mod_race_informal_support_ipv_nocov, variables = list("informal_support_prop" = "minmax"), vcov = "HC")
```

# Models side by side

Coefficients are beta coefficients,

```{r}
modelsummary::modelsummary(
  models = list(
    "IPV on race" = mod_race_ipv,
    "Social support on race" = mod_race_informal_support,
    "IPV on race and social support" = mod_race_informal_support_ipv
  ),
  estimate = "estimate",
  stars = TRUE,
  statistic = c("conf.int", "p.value"),
  vcov = sandwich::vcovHC
)
```

# Mediation Analysis

```{r, warning = FALSE}
mod_mediation <- mediation::mediate(
  model.m = mod_race_informal_support,
  model.y = mod_race_informal_support_ipv,
  sims = 2000,
  treat = "m_race",
  mediator = "informal_support_prop", 
  robustSE = TRUE
)

# summary to get the p-values
summary(mod_mediation)

# code solution to get unrounded upper confidence intervals
# source: https://stackoverflow.com/questions/53850958/r-mediation-package-digit-behind-comma
trace(mediation:::print.summary.mediate, 
      at = 11,
      tracer = quote({
        printCoefmat <- function(x, digits) {
          p <- x[, 4] #p-values seem to be stored rounded
          x[, 1:3] <- sprintf("%.6f", x[, 1:3])
          x[, 4] <- "ignore" # changed
          print(x, quote = FALSE, right = TRUE)
        } 
      }),
      print = FALSE)
mediation:::print.summary.mediate(summary(mod_mediation))

untrace(mediation:::print.summary.mediate)
```

Without including covariates

```{r}
mod_mediation <- mediation::mediate(
  model.m = mod_race_informal_support_nocov,
  model.y = mod_race_informal_support_ipv_nocov,
  sims = 2000,
  treat = "m_race",
  mediator = "informal_support_prop", 
  robustSE = TRUE
)

# summary to get the p-values
summary(mod_mediation)

# code solution to get unrounded upper confidence intervals
# source: https://stackoverflow.com/questions/53850958/r-mediation-package-digit-behind-comma
trace(mediation:::print.summary.mediate, 
      at = 11,
      tracer = quote({
        printCoefmat <- function(x, digits) {
          p <- x[, 4] #p-values seem to be stored rounded
          x[, 1:3] <- sprintf("%.6f", x[, 1:3])
          x[, 4] <- "ignore" # changed
          print(x, quote = FALSE, right = TRUE)
        } 
      }),
      print = FALSE)
mediation:::print.summary.mediate(summary(mod_mediation))

untrace(mediation:::print.summary.mediate)
```
