---
title: "Sample Comparative Analysis"
format: docx
editor: visual
execute:
  echo: false
  message: false
---

In this document we run some exploratory analyses to look into the differences in results for the national and not national samples. Inclusion criteria are otherwise the same.

```{r}
library(here)
library(tidyverse)
library(gtsummary)
library(marginaleffects)
library(modelsummary)


dat_imputed <- readRDS(file = here::here("01_data-processing", "data_private", "data_final_imputed_cases.RDS")) |>
  select(
    starts_with("m_"),
    ends_with("prop"),
    -contains("sample")
  )|>
  dplyr::mutate(
    ipv_binary = ifelse(ipv_prop > 0, 1, 0),
    informal_support_binary = ifelse(informal_support_prop == 1, 1, 0), 
    sample = "national"
  )

dat_imputed_not_national <- readRDS(file = here::here("01_data-processing", "data_private", "data_final_imputed_cases_not_national.RDS")) |>
  select(
    starts_with("m_"),
    ends_with("prop"),
    -contains("sample")
  )|>
  dplyr::mutate(
    ipv_binary = ifelse(ipv_prop > 0, 1, 0),
    informal_support_binary = ifelse(informal_support_prop == 1, 1, 0), 
    sample = "not national"
  )

dat_imputed_together <- dat_imputed |> 
  dplyr::bind_rows(dat_imputed_not_national)
```

# Summary

-   IPV on Race:

    -   no covariates: results practically the same; formal tests of interactions not significant

    -   with covariates: results practically the same; formal tests of interactions not significant

-   Informal support on Race:

    -   no covariates: very weak evidence that the relationship is stronger in the national sample

    -   with covariates: weak evidence that the relationship is stronger in the national sample; in the not-national sample, Black women have slightly *more* supports, while they have *fewer* supports in the national sample

-   IPV on Race and Informal Support:

    -   no covariates: the effect of informal support is stronger in the national sample, and indistinguishable from 0 in the non-national sample
    
    -   with covariates: the effect of informal support is stronger in the national sample, and indistinguishable from 0 in the non-national sample

# IPV on Race

First, is the rate of IPV in general different across samples?

```{r}
m1 <- lm(ipv_prop ~ 0 + sample,
         data = dat_imputed_together)

summary(m1)

marginaleffects::avg_predictions(
  m1,
  hypothesis = "pairwise",
  variables = "sample"
)
```

The rates are very very similar.

Is the effect of race on IPV (without covariates) different across samples?

```{r}
m2 <- lm(
  ipv_prop ~ m_race*sample,
  data = dat_imputed_together
)

summary(m2)

marginaleffects::avg_comparisons(
  m2,
  variables = "m_race",
  by = "sample"
)

marginaleffects::plot_comparisons(
  m2,
  variables = "m_race",
  by = "sample"
)
```

We can see that IPV is a little higher for Black women in both samples, with no meaningful difference between samples.

To see what would happen if we had *not* filtered out the not-national sample, we will run our models of IPV on race and all the covariates with the two separate samples and also together and look at the estimates.

```{r}
m3_nat <- lm(
  formula = ipv_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed,
)

m3_notnat <- lm(
  formula = ipv_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_not_national,
)

m3_both <- lm(
  formula = ipv_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_together,
)

modelsummary::modelsummary(
  models = list("National" = m3_nat,
                "Not National" = m3_notnat,
                "Together" = m3_both),
  statistic = c("conf.int", "p = {p.value}"),
  vcov = sandwich::vcovHC
)
```

We notice that the estimate for the effect of race is 10 times larger in the non-national sample, but the confidence interval is very large too, more than overlapping with the CI from the national sample. Still, we can run a model with an interaction between race and sample and all the covariates.

```{r}
m4 <- lm(
  formula = ipv_prop ~ m_race*sample +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_together,
)

summary(m4)

marginaleffects::plot_comparisons(
  m4,
  variables = "m_race",
  by = "sample"
)
```

Here, too, we see no evidence that the non-national sample diverges in any interesting way from the national sample.

# Informal support on race

First, is the rate of informal support in general different across samples?

```{r}
m5 <- lm(informal_support_prop ~ 0 + sample,
         data = dat_imputed_together)

summary(m5)

marginaleffects::avg_predictions(
  m5,
  hypothesis = "pairwise",
  variables = "sample"
)
```

The rates are very similar.

Is the effect of race on informal support (without covs) very different across samples?

```{r}
m6 <- lm(
  informal_support_prop ~ m_race*sample,
  data = dat_imputed_together
)

summary(m6)

marginaleffects::avg_comparisons(
  m6,
  variables = "m_race",
  by = "sample"
)

marginaleffects::plot_comparisons(
  m6,
  variables = "m_race",
  by = "sample"
)
```

Here we see slightly bigger differences. It seems that in the national sample there is a stronger effect of race on informal support, although the interaction is not significant.

To see what would happen if we had *not* filtered out the not-national sample, we will run our models of informal support on race and all the covariates with the two separate samples and also together and look at the estimates.

```{r}
m7_nat <- lm(
  formula = informal_support_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed,
)

m7_notnat <- lm(
  formula = informal_support_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_not_national,
)

m7_both <- lm(
  formula = informal_support_prop ~ m_race +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_together,
)

modelsummary::modelsummary(
  models = list("National" = m7_nat,
                "Not National" = m7_notnat,
                "Together" = m7_both),
  statistic = c("conf.int", "p = {p.value}"),
  vcov = sandwich::vcovHC
)
```

Comparing estimates and R^2^, we see that our model does slightly *worse* in the not-national sample — it appears that our covariates do not explain informal support as well in the not-national sample as they do in the national sample, but this difference is rather small, and the RMSE is the same.

Let's also check for an interaction between race and sample.

```{r}
m8 <- lm(
  formula = informal_support_prop ~ m_race*sample +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_together,
)

summary(m8)


marginaleffects::avg_comparisons(
  m8,
  variables = "m_race",
  by = "sample"
)

marginaleffects::avg_comparisons(
  m8,
  variables = "m_race",
  by = "sample",
  hypothesis = "pairwise"
)

marginaleffects::plot_comparisons(
  m8,
  variables = "m_race",
  by = "sample"
)
```

Here we do find an interaction. In the national sample Black women have fewer social supports, while in the not national sample they have *more* social supports (but this latter effect is not signficant). Further, we find a signficant interaction, whereas the difference between Black and White women is 0.04 points smaller in the national sample.

# IPV on Race and Informal Support

Next we look at models predicting IPV that include both race and informal support. 

Are the effect of race and informal support on IPV (without covariates) different across samples?

```{r}
m9 <- lm(
  ipv_prop ~ (m_race + informal_support_prop)*sample ,
  data = dat_imputed_together
)

summary(m9)

marginaleffects::avg_comparisons(
  m9,
  variables = "m_race",
  by = "sample"
)

marginaleffects::avg_comparisons(
  m9,
  variables = list("informal_support_prop" = "minmax"),
  by = "sample"
)

marginaleffects::plot_comparisons(
  m9,
  variables = list("informal_support_prop" = "minmax"),
  by = "sample"
)
```

The interaction between sample and informal support is significant. We find a stronger protective effect of informal support in the national sample.



To see what would happen if we had *not* filtered out the not-national sample, we will run our models of IPV on race and all the covariates with the two separate samples and also together and look at the estimates.

```{r}
m10_nat <- lm(
  formula = ipv_prop ~ m_race + informal_support_prop +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed,
)

m10_notnat <- lm(
  formula = ipv_prop ~ m_race + informal_support_prop +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_not_national,
)

m10_both <- lm(
  formula = ipv_prop ~ m_race + informal_support_prop +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_together,
)

modelsummary::modelsummary(
  models = list("National" = m10_nat,
                "Not National" = m10_notnat,
                "Together" = m10_both),
  statistic = c("conf.int", "p = {p.value}"),
  vcov = sandwich::vcovHC
)
```

Here we see again that the effect of informal support is larger in the national sample. This is further confirmed if we run a model interacting race and sample and informal support and sample.

```{r}
m11 <- lm(
  formula = ipv_prop ~ (m_race + informal_support_prop)*sample +
    m_age + m_education + m_alcohol + m_drugs +
    m_employment + m_children + m_household_income +
    m_home + m_welfare_last_year + m_health + m_religious,
  data = dat_imputed_together,
)

summary(m11)

marginaleffects::plot_comparisons(
  m11,
  variables = list("informal_support_prop" = "minmax"),
  by = "sample"
)
```

Here, too, we see no evidence that the non-national sample diverges in any interesting way from the national sample.
